Inference of Bifurcations\\with Differentiable Continuation

### 2021-05-14 docs/article.tex

\subsection{Genetic Toggle Switch | \textit{in progress}}
In this section we optimise a model where the states share a Hill function relationship; these models often emerge from mass action kinetics and are used to model species concentrations. By not restricting the sign of the coefficients $a_1,a_2$ we can recover both activator and inhibitor relationships.
\begin{equation}
    \partial_t u_1 = \frac{\varepsilon_1 + a_1 u_2^2} { k_1^2 + u_2^2 } - \mu_1 u_1 \quad
    \partial_t u_2 = \frac{p + a_2 u_1^2} { k_2^2 + u_1^2 } - \mu_2 u_2
\end{equation}
Figure \ref{fig:two-state-optima} shows a reduced dimensionality plot of the optimal parameter basins, represented as point clouds. $N$ distinct clusters are observed, each corresponding to a kinetically different model regions that are qualitatively equivalent.

>>>>

\subsection{Genetic Toggle Switch | \textit{in progress}}
In this section we optimise a model where the states share a Hill function relationship; these models often emerge from mass action kinetics and are used to model species concentrations. By not restricting the sign of the coefficients $a_1,a_2$ we can recover both activator and inhibitor relationships.
\begin{equation}
    \partial_t u_1 = \frac{\varepsilon_1 + a_1 u_2^2} { k_1^2 + u_2^2 } - \mu_1 u_1 \quad
    \partial_t u_2 = \frac{p + a_2 u_1^2} { k_2^2 + u_1^2 } - \mu_2 u_2
    \label{eq:two-state}
\end{equation}
Figure \ref{fig:two-state-optima} shows a reduced dimensionality plot of the optimal parameter basins, represented as point clouds. 14 distinct clusters are observed, each corresponding to a kinetically different model regions that are qualitatively equivalent.

\begin{figure}
\centering
\includegraphics[width=11cm]{two-state-optima}
\caption{Reduced dimensionality plot of optimal $\theta^*$ for the two state model \eqref{eq:two-state} for $\targets=\{4,5\}$}
\label{fig:two-state-optima}
\end{figure}
